Was Devon Allen Unjustly Disqualified at the 2022 World Track and Field Championships?

### 2023-03-25 Manuscript/manuscript.tex
added paper structure

@@

%\bigskip
\noindent\sc{Keywords}:
Devon Allen, Reaction Time, Seiko, 2022 World Track and Field Championships

@@

@@

@@

>>>>

  \jy{This is only the background. An abstract also needs to summarize the contributions.}
%\bigskip
\noindent\sc{Keywords}:
Devon Allen, Reaction Time, Seiko, 2022 World Track and Field Championships

@@

@@

\jy{Turn on column numbers in your editor to keep line width under 80.}

@@

\jy{use the following structure and flow:
  1) A paragraph to tell the story;
  2) A paragraph on informal statistical analyses on the internet/social media;
  3) A paragraph on scholarly articles on reaction time in the literature;
  4) A paragraph on what's new: methods; results.
  5) A paragraph of roadmap.}

@@

\section{Data} \label{sec:data}

\jy{Describe you data types; give details on sources; introduce notations for
  both types of data
  present exploratory plots.}

\section{Methods} \label{sec:meth}

\jy{set up the models/methods using the notations from last section; cite the
  right references.}

\subsection{GLMM}

\jy{explain the gamma model in details}

\subsection{Rank-based comparison for Clustered}

\section{Results}

\jy{Presents and discuss the results here}

\section{Concluding Remarks}

\jy{summarize your findings; discuss limitations and possible future works.}
